---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
title: "Summary of Yearly Comtrade Data, Quantity Trade Gap"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=0.75in
fontfamily: mathpazo
fontsize: 10pt
# spacing: double
endnote: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, fig.width=5, fig.height=3, fig.align="center", fig.path='Figs/')
library(data.table)
library(plyr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(lfe)
library(gridExtra)
library(cowplot)
library(knitr)
library(pander)

setwd(dirname(path.expand("~")))

DataPath <- file.path(paste(getwd(),"Dropbox/Customs Evasion", sep="/"))
CodePath <- file.path(paste(getwd(),"Documents/comtrade", sep = "/"))

theme_set(theme_cowplot(font_size=10))

```

This analysis is for the full 2012-2016 yearly Comtrade data using the HS2012 classification. 


```{r data clean, eval=FALSE}

load(paste(DataPath,"Analysis Data/hs12_12.Rda", sep = "/"))
hs12_12 <- hs12_12[!is.na(Qty_log_gap)]
hs12_12 <- hs12_12[!is.infinite(Qty_log_gap)]

load(paste(DataPath,"Analysis Data/hs12_13.Rda", sep = "/"))
hs12_13 <- hs12_13[!is.na(Qty_log_gap)]
hs12_13 <- hs12_13[!is.infinite(Qty_log_gap)]

load(paste(DataPath,"Analysis Data/hs12_14.Rda", sep = "/"))
hs12_14 <- hs12_14[!is.na(Qty_log_gap)]
hs12_14 <- hs12_14[!is.infinite(Qty_log_gap)]

load(paste(DataPath,"Analysis Data/hs12_15.Rda", sep = "/"))
hs12_15 <- hs12_15[!is.na(Qty_log_gap)]
hs12_15 <- hs12_15[!is.infinite(Qty_log_gap)]

load(paste(DataPath,"Analysis Data/hs12_16.Rda", sep = "/"))
hs12_16 <- hs12_16[!is.na(Qty_log_gap)]
hs12_16 <- hs12_16[!is.infinite(Qty_log_gap)]

hs12_qty <- do.call("rbind", list(hs12_12, hs12_13, hs12_14, hs12_15, hs12_16))
rm(hs12_12, hs12_13, hs12_14, hs12_15, hs12_16)

save(hs12_qty,file = paste(DataPath,"Analysis Data","hs12_qty.Rda", sep = "/"))

rm(hs12_qty)

```

#Quantity Trade Gap
The difference between what the exporting country reports and what the importing country reports in netweight
(kg).

##Coverage
```{r qty_coverage, eval=TRUE}

options(digits=2)

#For each year, how many product x o-d pairs / all possible product x o-d pairs?

load(paste(DataPath,"Analysis Data/hs12_qty.Rda", sep = "/"))
hs12_qty <- hs12_qty[, .(Period, `Commodity Code`, Importer, Exporter, Log_gap)]

product <- hs12_qty[, uniqueN(`Commodity Code`)]
product_year <- hs12_qty[, uniqueN(`Commodity Code`), by=Period]
product_year <- rename(product_year, Products = V1)

pair <- unique(setDT(hs12_qty), by = c("Importer", "Exporter"))
pair <- pair[, .N]
pair_year <- unique(setDT(hs12_qty), by = c("Importer", "Exporter", "Period"))
pair_year <- pair_year[, .N, by=Period]
pair_year <- rename(pair_year, Pairs = N)

year_coverage <- merge(product_year, pair_year)
year_coverage$Total_products <- product
year_coverage$Total_pairs <- pair

year_coverage$Coverage <- (year_coverage$Products*year_coverage$Pairs)/
  (year_coverage$Total_products*year_coverage$Total_pair)

pander(year_coverage)
rm(pair_year, product_year, year_coverage)

#For each product, how many year x o-d pairs / all possible year x o-d pairs?

year <- hs12_qty[, uniqueN(`Period`)]
year_product <- hs12_qty[, uniqueN(`Period`), by=`Commodity Code`]
year_product <- rename(year_product, Years = V1)

pair_product <- unique(setDT(hs12_qty), by = c("Importer", "Exporter", "Commodity Code"))
pair_product <- pair_product[, .N, by= .(`Commodity Code`)]
pair_product <- rename(pair_product, Pairs = N)

product_coverage <- merge(year_product, pair_product)
product_coverage$Total_years <- year
product_coverage$Total_pairs <- pair

product_coverage$Coverage <- (product_coverage$Years*product_coverage$Pairs)/
  (product_coverage$Total_years*product_coverage$Total_pairs)

pander(product_coverage[order(Coverage)][1:10])
pander(product_coverage[order(-Coverage)][1:10])

rm(year_product, pair_product, product_coverage)

#For each o-d pair, how many year x product / all possible year x product?

product_pair <- hs12_qty[, uniqueN(`Commodity Code`), by = c("Importer", "Exporter")]
product_pair <- rename(product_pair, Products = V1)

year_pair <- hs12_qty[, uniqueN(`Period`), by = c("Importer", "Exporter")]
year_pair <- rename(year_pair, Years = V1)

pair_coverage <- merge(product_pair, year_pair, by = c("Importer", "Exporter"))
pair_coverage$T_products <- product
pair_coverage$T_years <- year

pair_coverage$Coverage <- (pair_coverage$Products*pair_coverage$Years)/
  (pair_coverage$T_products*pair_coverage$T_years)

pair_coverage$Exporter <- strtrim(pair_coverage$Exporter, 15)
pander(pair_coverage[order(Coverage)][1:10])
pander(pair_coverage[order(-Coverage)][1:10])

rm(product_pair, year_pair, pair_coverage, pair, product, year, hs12_qty)

```


##Quantity trade gap over time 
```{r qty_time, eval=TRUE}

load(paste(DataPath,"Analysis Data/hs12_qty.Rda", sep = "/"))

hs12_qty <- hs12_qty[, .(Period, `Commodity Code`, Importer, Exporter, Qty_log_gap)]

hs12_qty$Period <- as.Date(hs12_qty$Period, "%Y")
hs12_qty$Period <- floor_date(hs12_qty$Period,"year")

periods <- hs12_qty[, .(mean = as.double(mean(Qty_log_gap)),
                          median = as.double(median(Qty_log_gap)),
                          p25 = as.double(quantile(Qty_log_gap,.25)),
                          p75 = as.double(quantile(Qty_log_gap,.75))
),
by=Period]

periods <- melt(periods, id = 'Period')
periods$variable <- factor(periods$variable, levels = c("p25","p75","median","mean"))

ggplot(data=periods ) +
  geom_line(data=periods, aes(x = Period, y = value, colour = variable, size=variable)) +
  scale_colour_manual(values=c("grey","grey","black","royalblue4")) +
  background_grid(major = 'y', minor = "none") +
  scale_size_manual(values = c(1,1,1.1,1.25)) +
  scale_y_continuous(expand = c(0, 0), limits = c(-1.5,1), minor_breaks = NULL) +
  xlab(label = "") +
  ylab(label = "Quantity gap") +
  labs(title="Quantity Gap Over Time")

#Across products?
products <- hs12_qty[, .(mean = as.double(mean(Qty_log_gap)),
                           median = as.double(median(Qty_log_gap)),
                           p25 = as.double(quantile(Qty_log_gap,.25)),
                           p75 = as.double(quantile(Qty_log_gap,.75))
),
by= `Commodity Code`]

ggplot(data=products, aes(mean)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,3000), minor_breaks = NULL) +
  labs(title="Mean Quantity Gap Across Products") +
  labs(x="Quantity gap", y="Number of products")

ggplot(data=products, aes(median)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,6000)) +
  labs(title="Median Quantity Gap Across Products") +
  labs(x="Quantity gap", y="Number of products")

ggplot(data=products, aes(p25)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,1000),  minor_breaks = NULL) +
  labs(title="25th Percentile Quantity Gap Across Products") +
  labs(x="Quantity gap", y="Number of products")

ggplot(data=products, aes(p75)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0),  limits = c(0, 2000), minor_breaks = NULL) +
  labs(title="75th Percentile Quantity Gap Across Products") +
  labs(x="Quantity gap", y="Number of products")

#Across countries?
countries <- hs12_qty[, .(mean = as.double(mean(Qty_log_gap)),
                            median = as.double(median(Qty_log_gap)),
                            p25 = as.double(quantile(Qty_log_gap,.25)),
                            p75 = as.double(quantile(Qty_log_gap,.75))
),
by= c("Importer", "Exporter")]

ggplot(data=countries, aes(mean)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 8000),  minor_breaks = NULL) +
  labs(title="Mean Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

ggplot(data=countries, aes(median)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 12000),  minor_breaks = NULL) +
  labs(title="Median Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

ggplot(data=countries, aes(p25)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 6000),  minor_breaks = NULL) +
  labs(title="25th Percentile Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

ggplot(data=countries, aes(p75)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 8000),  minor_breaks = NULL) +
  labs(title="75th Percentile Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

rm(periods, products, countries, hs12_qty)
```

##Year coefficients controlling for product codes and country pairs 
```{r qty_years_reg, eval=TRUE}

load(paste(DataPath,"Analysis Data/hs12_qty.Rda", sep = "/"))

hs12_qty <- hs12_qty[, .(Period, `Commodity Code`, `Reporter Code`, `Partner Code`, Qty_log_gap)]

hs12_qty$Period <- as.Date(hs12_qty$Period, "%Y")
hs12_qty$Period <- floor_date(hs12_qty$Period,"year")

hs12_qty$Period.f <- factor(hs12_qty$Period)
hs12_qty$Products.f <- factor(hs12_qty$`Commodity Code`)

hs12_qty$Importer.f <- factor(hs12_qty$`Reporter Code`)
hs12_qty$Exporter.f <- factor(hs12_qty$`Partner Code`)
hs12_qty$Pairs.f <- with(hs12_qty, interaction(Importer.f, Exporter.f))

hs12_qty <- hs12_qty[, .(Period, Qty_log_gap, Period.f, Products.f, Pairs.f)]

reg <- felm(Qty_log_gap ~ 1 | Period.f + Products.f + Pairs.f,
            data = hs12_qty,
            exactDOF = FALSE,
            keepX = FALSE,
            keepCX = FALSE)

fes <- getfe(reg,
             se=TRUE,
             bN = 50
)

periodfes <- subset(fes,fe == "Period.f")

periodfes$ci_ub <- periodfes$effect + (1.96 * periodfes$se)
periodfes$ci_lb <- periodfes$effect - (1.96 * periodfes$se)
periodfes <- merge(periodfes,unique(hs12_qty[,list(Period,Period.f)]),
                   by.x = "idx",by.y="Period.f")
periodfes <- rename(periodfes, period = Period)

ggplot(data = periodfes, aes(period,effect)) +
  geom_errorbar(aes(ymin = ci_lb, ymax = ci_ub), color = "grey35") +
  geom_line(color = "royalblue4", size = 1) +
  geom_point(color = "royalblue4") +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(-.050,.050), minor_breaks = NULL) +
  xlab(label = "") +
  ylab(label = "Quantity gap") +
  labs(title = "Quantity gap Over Time, Controlling for Product/Country Pairs")


productfes <- subset(fes,fe == "Products.f")
productfes <- productfes[,c("effect","idx")]

ggplot(data=productfes, aes(effect)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,2500), minor_breaks = NULL) +
  labs(title="Mean Trade Gap Across Products, Controlling for Country Pairs/Years") +
  labs(x="Trade gap", y="Number of products")

pairfes <- subset(fes,fe == "Pairs.f")
pairfes <- pairfes[,c("effect","idx")]

ggplot(data=pairfes, aes(effect)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,8000), minor_breaks = NULL) +
  labs(title="Mean Quantity Gap Across Country Pairs, Controlling for Products/Years") +
  labs(x="Quantity gap", y="Number of country pairs")

rm(fes, hs12_qty, pairfes, periodfes, productfes, reg)

```

##What data is missing? 

The first table looks at how many product x year x partner combinations each country reported as exports (`Reported Exports`), relative to the number of combinations that the same country was reported as a partner (`World Imports`). The second table repeats the first, but looking at imports.  

```{r missing, eval=TRUE}
#yearXproduct exports reported by country, relative to imports to country reported by world

load(paste(DataPath,"Analysis Data/imports_full12.Rda", sep = "/"))

imports_full12 <- rename(imports_full12, "Import Netweight (kg)" = "Netweight (kg)")
imports_full12 <- imports_full12[, 
                      .(Period, Reporter, Partner, `Commodity Code`, `Import Netweight (kg)`)]

imports_full12[`Import Netweight (kg)`==""]$`Import Netweight (kg)` <- NA

load(paste(DataPath,"Analysis Data/exports_full12.Rda", sep = "/"))

exports <- rename(exports, "Export Netweight (kg)" = "Netweight (kg)")
exports <- exports[, .(Period, Reporter, Partner, `Commodity Code`, `Export Netweight (kg)`)]

exports[`Export Netweight (kg)`==""]$`Export Netweight (kg)` <- NA


rep_ex <- exports[!is.na(`Export Netweight (kg)`), unique(`Commodity Code`), 
                  by = c("Reporter", "Period", "Partner")]
rep_ex <- rep_ex[, .N, by = "Reporter"]
rep_ex <- rename(rep_ex, "Reported Exports" = "N") 

rep_ex2 <- imports_full12[!is.na(`Import Netweight (kg)`), unique(`Commodity Code`), 
                          by = c("Partner", "Period", "Reporter")]
rep_ex2 <- rep_ex2[, .N, by = "Partner"]
rep_ex2 <- rename(rep_ex2, "World Imports" = "N") 

rep_ex <- merge(rep_ex, rep_ex2, by.x = c("Reporter"), by.y = "Partner", all = T)

rep_ex[is.na(rep_ex)] <- 0
rep_ex$Share_Present <- rep_ex$`Reported Exports` / rep_ex$`World Imports`

rep_ex <- rep_ex[order(Share_Present)]
rep_ex$Reporter <- strtrim(rep_ex$Reporter, 15)
print(rep_ex, nrow=245)

rm(rep_ex, rep_ex2)

#yearXproduct imports reported by country, relative to exports to country reported by world

rep_im <- imports_full12[!is.na(`Import Netweight (kg)`), unique(`Commodity Code`), 
                         by = c("Reporter", "Period", "Partner")]
rep_im <- rep_im[, .N, by = "Reporter"]
rep_im <- rename(rep_im, "Reported Imports" = "N") 

rep_im2 <- exports[!is.na(`Export Netweight (kg)`), unique(`Commodity Code`), 
                   by = c("Partner", "Period", "Reporter")]
rep_im2 <- rep_im2[, .N, by = "Partner"]
rep_im2 <- rename(rep_im2, "World Exports" = "N") 

rep_im <- merge(rep_im, rep_im2, by.x = c("Reporter"), by.y = "Partner", all = T)

rep_im[is.na(rep_im)] <- 0
rep_im$Share_Present <- rep_im$`Reported Imports` / rep_im$`World Exports`

rep_im <- rep_im[order(Share_Present)]
rep_im$Reporter <- strtrim(rep_im$Reporter, 15)
print(rep_im, nrow=245)

rm(rep_im, rep_im2, exports, imports_full12)
```

###Origin x year combinations, per commodity code
The following tables look at the number of origin x year combinations per reporter (`Reporter Pairs`) vs the number of combinations per partner (`Partner Pairs`) for reported exports and then reported imports.

```{r missing_code, eval=TRUE}
#For each product how many origin X month combinations
load(paste(DataPath,"Analysis Data/imports_full12.Rda", sep = "/"))

imports_full12 <- rename(imports_full12, "Import Netweight (kg)" = "Netweight (kg)")
imports_full12 <- imports_full12[, 
                .(Period, Reporter, Partner, `Commodity Code`, Commodity, `Import Netweight (kg)`)]

imports_full12[`Import Netweight (kg)`==""]$`Import Netweight (kg)` <- NA

load(paste(DataPath,"Analysis Data/exports_full12.Rda", sep = "/"))

exports <- rename(exports, "Export Netweight (kg)" = "Netweight (kg)")
exports <- exports[, 
            .(Period, Reporter, Partner, `Commodity Code`, Commodity, `Export Netweight (kg)`)]

exports[`Export Netweight (kg)`==""]$`Export Netweight (kg)` <- NA

prod_ex <- exports[!is.na(`Export Netweight (kg)`), unique(`Reporter`), 
                   by = c("Commodity", "Period")]
prod_ex <- prod_ex[, .N, by = "Commodity"]
prod_ex <- rename(prod_ex, "Reporter Pairs" = "N") 

prod_expartner <- imports_full12[!is.na(`Import Netweight (kg)`), unique(`Partner`), 
                                 by = c("Commodity", "Period")]
prod_expartner <- prod_expartner[, .N, by = "Commodity"]
prod_expartner <- rename(prod_expartner, "Partner Pairs" = "N") 

prod_ex <- merge(prod_ex, prod_expartner, by = c("Commodity"), all = T) 

prod_ex$Share <- prod_ex$`Reporter Pairs` / prod_ex$`Partner Pairs`

prod_ex$Commodity <- strtrim(prod_ex$Commodity, 50)
pander(prod_ex[order(Share)][1:25])
pander(prod_ex[order(-Share)][1:25])

rm(prod_ex, prod_expartner)

prod_im <- imports_full12[!is.na(`Import Netweight (kg)`), unique(`Reporter`), 
                          by = c("Commodity", "Period")]
prod_im <- prod_im[, .N, by = "Commodity"]
prod_im <- rename(prod_im, "Reporter Pairs" = "N") 

prod_impartner <- exports[!is.na(`Export Netweight (kg)`), unique(`Partner`), 
                          by = c("Commodity", "Period")]
prod_impartner <- prod_impartner[, .N, by = "Commodity"]
prod_impartner <- rename(prod_impartner, "Partner Pairs" = "N") 

prod_im <- merge(prod_im, prod_impartner, by = c("Commodity"), all = T)

prod_im$Share <- prod_im$`Reporter Pairs` / prod_im$`Partner Pairs`

prod_im$Commodity <- strtrim(prod_im$Commodity, 50)
pander(prod_im[order(Share)][1:25])
pander(prod_im[order(-Share)][1:25])

rm(prod_im, prod_impartner, exports, imports_full12)
```