---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
title: "Summary of Yearly Comtrade Data, HS 2012"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=0.75in
fontfamily: mathpazo
fontsize: 10pt
# spacing: double
endnote: no
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, fig.width=5, fig.height=3, fig.align="center", fig.path='Figs/')
library(data.table)
library(plyr)
library(ggplot2)
library(dplyr)
library(lubridate)
library(lfe)
library(gridExtra)
library(cowplot)
library(knitr)

setwd(dirname(path.expand("~")))

DataPath <- file.path(paste(getwd(),"Dropbox/BJ Customs Evasion", sep="/"))
CodePath <- file.path(paste(getwd(),"Documents/Comtrade", sep = "/"))

theme_set(theme_cowplot(font_size=10))

```

#Clean data and create trade gap variables
This is for a small subset of the UN Comtrade data: specifically, for years 2012-2016, products that start with a 0 in the HS 2012 classification system, and for countries that start with the letter "A" (Afghanistan) through "M" (Myanmar).

*Notes\:*

- *There are a lot of cases where country A has reported exports but country B has not reported anything. As much as half of the raw data becomes "missing" due to this. This seems consistent with Fisman/Wei (pg 4).*  

- *The raw data contains re-exports and re-imports. These amounts are also included in a country's regular exports/imports as imports from one country to itself. For example, France has re-imports that are also included in France's imports as `Reporter` = France and `Partner` = France. This doesn't affect this analysis because there is no matched reporter/partner pair, but they might affect our trade gap measure if they're actually imports from an unforseen place. More on re-exports **[at this link.](https://unstats.un.org/unsd/tradekb/Knowledgebase/Reexports-and-Reimports)** *  

```{r data clean, eval=FALSE}

#Keep product codes starting with "0" and country pairs starting with letters "A" through "M"
load(paste(DataPath,"Raw Data/Comtrade/Yearly/y_hs12/y_2012_hs12.Rda", sep = "/"))
y_2012_hs12 <- as.data.table(y_2012_hs12)

y_2012_hs12 <- subset(y_2012_hs12,substr(y_2012_hs12$`Commodity Code`,1,1)=='0')
y_2012_hs12 <- y_2012_hs12[grep("^[A-M]", y_2012_hs12$Reporter)]
y_2012_hs12 <- y_2012_hs12[grep("^[A-M]", y_2012_hs12$Partner)]

load(paste(DataPath,"Raw Data/Comtrade/Yearly/y_hs12/y_2013_hs12.Rda", sep = "/"))
y_2013_hs12 <- as.data.table(y_2013_hs12)

y_2013_hs12 <- subset(y_2013_hs12,substr(y_2013_hs12$`Commodity Code`,1,1)=='0')
y_2013_hs12 <- y_2013_hs12[grep("^[A-M]", y_2013_hs12$Reporter)]
y_2013_hs12 <- y_2013_hs12[grep("^[A-M]", y_2013_hs12$Partner)]

load(paste(DataPath,"Raw Data/Comtrade/Yearly/y_hs12/y_2014_hs12.Rda", sep = "/"))
y_2014_hs12 <- as.data.table(y_2014_hs12)

y_2014_hs12 <- subset(y_2014_hs12,substr(y_2014_hs12$`Commodity Code`,1,1)=='0')
y_2014_hs12 <- y_2014_hs12[grep("^[A-M]", y_2014_hs12$Reporter)]
y_2014_hs12 <- y_2014_hs12[grep("^[A-M]", y_2014_hs12$Partner)]

load(paste(DataPath,"Raw Data/Comtrade/Yearly/y_hs12/y_2015_hs12.Rda", sep = "/"))
y_2015_hs12 <- as.data.table(y_2015_hs12)

y_2015_hs12 <- subset(y_2015_hs12,substr(y_2015_hs12$`Commodity Code`,1,1)=='0')
y_2015_hs12 <- y_2015_hs12[grep("^[A-M]", y_2015_hs12$Reporter)]
y_2015_hs12 <- y_2015_hs12[grep("^[A-M]", y_2015_hs12$Partner)]

load(paste(DataPath,"Raw Data/Comtrade/Yearly/y_hs12/y_2016_hs12.Rda", sep = "/"))
y_2016_hs12 <- as.data.table(y_2016_hs12)

y_2016_hs12 <- subset(y_2016_hs12,substr(y_2016_hs12$`Commodity Code`,1,1)=='0')
y_2016_hs12 <- y_2016_hs12[grep("^[A-M]", y_2016_hs12$Reporter)]
y_2016_hs12 <- y_2016_hs12[grep("^[A-M]", y_2016_hs12$Partner)]

#Combine HS 2012 data
hs12 <- do.call("rbind", list(y_2012_hs12, y_2013_hs12, y_2014_hs12, y_2015_hs12, y_2016_hs12))

rm(y_2012_hs12, y_2013_hs12, y_2014_hs12, y_2015_hs12, y_2016_hs12)

#Create table where country is reporting imports
hs12im <- hs12[`Trade Flow Code`==1]

hs12im[ ,`:=`(Classification = NULL, Year = NULL, 
                  `Period Desc.` = NULL, `Is Leaf Code` = NULL, 
                  `Reporter ISO` = NULL, `Partner ISO` = NULL,
                  `Qty Unit Code` = NULL,  Flag = NULL
                  )]

hs12im <- rename(hs12im, "Import Value" = "Trade Value (US$)") 
hs12im <- rename(hs12im, "Import Qty Unit" = "Qty Unit")
hs12im <- rename(hs12im, "Import Qty" = "Qty")
hs12im <- rename(hs12im, "Import Netweight (kg)" = "Netweight (kg)")

#Create table where country is reporting exports
hs12ex <- hs12[`Trade Flow Code`==2]

hs12ex[ ,`:=`(Classification = NULL, Year = NULL, 
                  `Period Desc.` = NULL, `Is Leaf Code` = NULL, 
                  `Reporter ISO` = NULL, `Partner ISO` = NULL,
                  `Qty Unit Code` = NULL,  Flag = NULL
                  )]

hs12ex <- rename(hs12ex, "Export Value" = "Trade Value (US$)")
hs12ex <- rename(hs12ex, "Export Qty Unit" = "Qty Unit")
hs12ex <- rename(hs12ex, "Export Qty" = "Qty")
hs12ex <- rename(hs12ex, "Export Netweight (kg)" = "Netweight (kg)")

#Merge import and export tables together
hs12 <- merge(hs12im, hs12ex, 
             by.x=c("Period", "Aggregate Level", 
                    "Reporter Code", "Reporter", "Partner Code", "Partner", 
                    "Commodity Code", "Commodity"),
             by.y=c("Period", "Aggregate Level", 
                    "Partner Code", "Partner", "Reporter Code", "Reporter", 
                    "Commodity Code", "Commodity"),all=TRUE)

hs12 <- rename(hs12, "Importer" = "Reporter")
hs12 <- rename(hs12, "Exporter" = "Partner")

#Create variable of the trade value gap between what countries report
hs12$Raw_gap = hs12$`Export Value` - hs12$`Import Value`

#Create variable of the log trade value gap
hs12$Log_gap = log(hs12$`Export Value`) - log(hs12$`Import Value`)

#Create variable of the trade value gap as a ratio of total reported trade  
hs12$Gap_ratio = hs12$`Raw_gap`/(hs12$`Import Value` + hs12$`Export Value`)

#Repeat created variables but for the gap in quantity reported
hs12$`Export Netweight (kg)` <- as.numeric(hs12$`Export Netweight (kg)`)
hs12$`Import Netweight (kg)` <- as.numeric(hs12$`Import Netweight (kg)`)

hs12$Qty_raw_gap = hs12$`Export Netweight (kg)` - hs12$`Import Netweight (kg)`

hs12$Qty_log_gap = log(hs12$`Export Netweight (kg)`) - log(hs12$`Import Netweight (kg)`)

hs12$Qty_gap_ratio = hs12$`Qty_raw_gap`/
                    (hs12$`Export Netweight (kg)` + hs12$`Import Netweight (kg)`)

save(hs12,file = paste(DataPath,"Analysis Data","hs12.Rda", sep = "/"))
rm(hs12, hs12ex, hs12im)

```

#Value Trade Gap
The difference between what the exporting country reports and what the importing country reports in US dollars.

**Coverage**
```{r value_coverage, eval=TRUE}
load(paste(DataPath,"Analysis Data/hs12.Rda", sep = "/"))
hs12 <- as.data.table(hs12)

options(digits=2)

#Remove observations where one or more countries do not report imports/exports. 
#699,887 rows deleted. 
hs12 <- hs12[!is.na(Log_gap)]

#For each year, how many product*country pairs / all possible product*country pairs?

product <- hs12[, uniqueN(`Commodity Code`)]
product_year <- hs12[, uniqueN(`Commodity Code`), by=Period]
product_year <- rename(product_year, Products = V1)

pair <- unique(setDT(hs12), by = c("Importer", "Exporter"))
pair <- pair[, .N]
pair_year <- unique(setDT(hs12), by = c("Importer", "Exporter", "Period"))
pair_year <- pair_year[, .N, by=Period]
pair_year <- rename(pair_year, Pairs = N)

year_coverage <- merge(product_year, pair_year)
year_coverage$Total_products <- product
year_coverage$Total_pairs <- pair

year_coverage$Coverage <- (year_coverage$Products*year_coverage$Pairs)/
                          (year_coverage$Total_products*year_coverage$Total_pair)

year_coverage
rm(pair_year, product_year, year_coverage)

#For each product, how many year*country pairs / all possible year*country pairs?

year <- hs12[, uniqueN(`Period`)]
year_product <- hs12[, uniqueN(`Period`), by=`Commodity Code`]
year_product <- rename(year_product, Years = V1)

pair_product <- unique(setDT(hs12), by = c("Importer", "Exporter", "Commodity Code"))
pair_product <- pair_product[, .N, by= .(`Commodity Code`)]
pair_product <- rename(pair_product, Pairs = N)

product_coverage <- merge(year_product, pair_product)
product_coverage$Total_years <- year
product_coverage$Total_pairs <- pair

product_coverage$Coverage <- (product_coverage$Years*product_coverage$Pairs)/
  (product_coverage$Total_years*product_coverage$Total_pairs)

product_coverage[order(Coverage)][1:10]
product_coverage[order(-Coverage)][1:10]

rm(year_product, pair_product, product_coverage)

#For each country pair, how many year*product / all possible year*product?

product_pair <- hs12[, uniqueN(`Commodity Code`), by = c("Importer", "Exporter")]
product_pair <- rename(product_pair, Products = V1)

year_pair <- hs12[, uniqueN(`Period`), by = c("Importer", "Exporter")]
year_pair <- rename(year_pair, Years = V1)

pair_coverage <- merge(product_pair, year_pair, by = c("Importer", "Exporter"))
pair_coverage$T_products <- product
pair_coverage$T_years <- year

pair_coverage$Coverage <- (pair_coverage$Products*pair_coverage$Years)/
  (pair_coverage$T_products*pair_coverage$T_years)

pair_coverage$Exporter <- strtrim(pair_coverage$Exporter, 15)
pair_coverage[order(Coverage)][1:10]
pair_coverage[order(-Coverage)][1:10]

rm(product_pair, year_pair, pair_coverage, pair, product, year)

```


**Trade gap over time** 
```{r value_time, eval=TRUE}

#How has the trade gap changed over time?

hs12$Period <- as.Date(hs12$Period, "%Y")
hs12$Period <- floor_date(hs12$Period,"year")

periods <- hs12[, .(mean = as.double(mean(Log_gap)),
                    median = as.double(median(Log_gap)),
                    p25 = as.double(quantile(Log_gap,.25)),
                    p75 = as.double(quantile(Log_gap,.75))
),
by=Period]

periods <- melt(periods, id = 'Period')
periods$variable <- factor(periods$variable, levels = c("p25","p75","median","mean"))

ggplot(data=periods ) +
  geom_line(data=periods, aes(x = Period, y = value, colour = variable, size=variable)) +
  scale_colour_manual(values=c("grey","grey","black","royalblue4")) +
  background_grid(major = 'y', minor = "none") +
  scale_size_manual(values = c(1,1,1.1,1.25)) +
  scale_y_continuous(expand = c(0, 0), limits = c(-1,1), minor_breaks = NULL) +
  xlab(label = "") +
  ylab(label = "Value gap") +
  labs(title="Value Gap Over Time")
```

**Trade gap across products** 
```{r value_products, eval=TRUE}

#Across products?
products <- hs12[, .(mean = as.double(mean(Log_gap)),
                     median = as.double(median(Log_gap)),
                     p25 = as.double(quantile(Log_gap,.25)),
                     p75 = as.double(quantile(Log_gap,.75))
),
by= `Commodity Code`]

ggplot(data=products, aes(mean)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,150), minor_breaks = NULL) +
  labs(title="Mean Trade Gap Across Products") +
  labs(x="Trade gap", y="Number of products")

ggplot(data=products, aes(median)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,350),  breaks=seq(0, 350, 50)) +
  labs(title="Median Trade Gap Across Products") +
  labs(x="Trade gap", y="Number of products")

ggplot(data=products, aes(p25)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0),  limits = c(0,150), minor_breaks = NULL) +
  labs(title="25th Percentile Trade Gap Across Products") +
  labs(x="Trade gap", y="Number of products")

ggplot(data=products, aes(p75)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0),  limits = c(0, 150), minor_breaks = NULL) +
  labs(title="75th Percentile Trade Gap Across Products") +
  labs(x="Trade gap", y="Number of products")
```

**Trade gap across country pairs** 
```{r value_pairs, eval=TRUE}

#Across countries?
countries <- hs12[, .(mean = as.double(mean(Log_gap)),
                      median = as.double(median(Log_gap)),
                      p25 = as.double(quantile(Log_gap,.25)),
                      p75 = as.double(quantile(Log_gap,.75))
),
by= c("Importer", "Exporter")]

ggplot(data=countries, aes(mean)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1500),  minor_breaks = NULL) +
  labs(title="Mean Trade Gap Across Country Pairs") +
  labs(x="Trade gap", y="Number of pairs")

ggplot(data=countries, aes(median)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 2000),  minor_breaks = NULL) +
  labs(title="Median Trade Gap Across Country Pairs") +
  labs(x="Trade gap", y="Number of pairs")

ggplot(data=countries, aes(p25)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 1500),  minor_breaks = NULL) +
  labs(title="25th Percentile Trade Gap Across Country Pairs") +
  labs(x="Trade gap", y="Number of pairs")

ggplot(data=countries, aes(p75)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 2000),  minor_breaks = NULL) +
  labs(title="75th Percentile Trade Gap Across Country Pairs") +
  labs(x="Trade gap", y="Number of pairs")

rm(periods, products, countries)
```

**Year coefficients controlling for product codes and country pairs** 
```{r value_years_reg, eval=TRUE}

hs12$Period <- as.Date(hs12$Period, "%Y")
hs12$Period <- floor_date(hs12$Period,"year")

hs12$Period.f <- factor(hs12$Period)
hs12$Products.f <- factor(hs12$`Commodity Code`)

hs12$Importer.f <- factor(hs12$`Reporter Code`)
hs12$Exporter.f <- factor(hs12$`Partner Code`)
hs12$Pairs.f <- with(hs12, interaction(Importer.f, Exporter.f))

reg <- felm(Log_gap ~ 1 | Period.f + Products.f + Pairs.f,
            data = hs12,
            exactDOF = FALSE,
            keepX = FALSE,
            keepCX = FALSE)

fes <- getfe(reg,
             se=TRUE,
             bN = 50
)

periodfes <- subset(fes,fe == "Period.f")

periodfes$ci_ub <- periodfes$effect + (1.96 * periodfes$se)
periodfes$ci_lb <- periodfes$effect - (1.96 * periodfes$se)
periodfes <- merge(periodfes,unique(hs12[,list(Period,Period.f)]),by.x = "idx",by.y="Period.f")
periodfes <- rename(periodfes, period = Period)

ggplot(data = periodfes, aes(period,effect)) +
  geom_errorbar(aes(ymin = ci_lb, ymax = ci_ub), color = "grey35") +
  geom_line(color = "royalblue4", size = 1) +
  geom_point(color = "royalblue4") +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(-.050,.075), minor_breaks = NULL) +
  xlab(label = "") +
  ylab(label = "Trade gap") +
  labs(title = "Trade Gap Over Time, Controlling for Product/Country Pair")
```

Why the 2016 bump? Could it be something to do with how they revise value estimates when they get more data or convert to most recent HS classification?


**Product code coefficients controlling for country pairs and years** 
```{r value_products_reg, eval=TRUE}

productfes <- subset(fes,fe == "Products.f")
productfes <- productfes[,c("effect","idx")]

ggplot(data=productfes, aes(effect)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,150), minor_breaks = NULL) +
  labs(title="Trade Gap Across Products, Controlling for Country Pair/Year") +
  labs(x="Trade gap", y="Number of products")
```

**Country pair coefficients controlling for years and product codes** 
```{r value_pairs_reg, eval=TRUE}

pairfes <- subset(fes,fe == "Pairs.f")
pairfes <- pairfes[,c("effect","idx")]

ggplot(data=pairfes, aes(effect)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,1500), minor_breaks = NULL) +
  labs(title="Trade Gap Across Country Pairs, Controlling for Product/Year") +
  labs(x="Trade gap", y="Number of country pairs")

rm(fes, hs12, pairfes, periodfes, productfes, reg)

```

#Quantity Trade Gap
The difference between what the exporting country reports and what the importing country reports in netweight (kg). 

**Coverage**
```{r quantity_coverage, eval=TRUE}

options(digits=2)

load(paste(DataPath,"Analysis Data/hs12.Rda", sep = "/"))
hs12 <- as.data.table(hs12)

#Remove observations where one or more countries do not report quantities. 748,839 rows deleted. 
hs12 <- hs12[!is.na(Qty_log_gap)]

#There are 411 instances where `qty_log_gap` = inf. 
#I removed them -- something else we should do?
hs12 <- hs12[!is.infinite(Qty_log_gap)]

#For each year, how many product*country pairs / all possible product*country pairs?

product <- hs12[, uniqueN(`Commodity Code`)]
product_year <- hs12[, uniqueN(`Commodity Code`), by=Period]
product_year <- rename(product_year, Products = V1)

pair <- unique(setDT(hs12), by = c("Importer", "Exporter"))
pair <- pair[, .N]
pair_year <- unique(setDT(hs12), by = c("Importer", "Exporter", "Period"))
pair_year <- pair_year[, .N, by=Period]
pair_year <- rename(pair_year, Pairs = N)

year_coverage <- merge(product_year, pair_year)
year_coverage$Total_products <- product
year_coverage$Total_pairs <- pair

year_coverage$Coverage <- (year_coverage$Products*year_coverage$Pairs)/
  (year_coverage$Total_products*year_coverage$Total_pair)

year_coverage
rm(pair_year, product_year, year_coverage)

#For each product, how many year*country pairs / all possible year*country pairs?

year <- hs12[, uniqueN(`Period`)]
year_product <- hs12[, uniqueN(`Period`), by=`Commodity Code`]
year_product <- rename(year_product, Years = V1)

pair_product <- unique(setDT(hs12), by = c("Importer", "Exporter", "Commodity Code"))
pair_product <- pair_product[, .N, by= .(`Commodity Code`)]
pair_product <- rename(pair_product, Pairs = N)

product_coverage <- merge(year_product, pair_product)
product_coverage$Total_years <- year
product_coverage$Total_pairs <- pair

product_coverage$Coverage <- (product_coverage$Years*product_coverage$Pairs)/
  (product_coverage$Total_years*product_coverage$Total_pairs)

#Note: Quantity is not reported at the two-digit level
product_coverage[order(Coverage)][1:10]
product_coverage[order(-Coverage)][1:10]

rm(year_product, pair_product, product_coverage)

#For each country pair, how many year*product / all possible year*product?

product_pair <- hs12[, uniqueN(`Commodity Code`), by = c("Importer", "Exporter")]
product_pair <- rename(product_pair, Products = V1)

year_pair <- hs12[, uniqueN(`Period`), by = c("Importer", "Exporter")]
year_pair <- rename(year_pair, Years = V1)

pair_coverage <- merge(product_pair, year_pair, by = c("Importer", "Exporter"))
pair_coverage$T_products <- product
pair_coverage$T_years <- year

pair_coverage$Coverage <- (pair_coverage$Products*pair_coverage$Years)/
  (pair_coverage$T_products*pair_coverage$T_years)

pair_coverage$Exporter <- strtrim(pair_coverage$Exporter, 15)
pair_coverage[order(Coverage)][1:10]
pair_coverage[order(-Coverage)][1:10]

rm(product_pair, year_pair, pair_coverage, pair, product, year)
```

**Quantity trade gap over time** 
```{r quantity_time, eval=TRUE}

hs12$Period <- as.Date(hs12$Period, "%Y")
hs12$Period <- floor_date(hs12$Period,"year")


periods <- hs12[, .(mean = as.double(mean(Qty_log_gap)),
                    median = as.double(median(Qty_log_gap)),
                    p25 = as.double(quantile(Qty_log_gap,.25)),
                    p75 = as.double(quantile(Qty_log_gap,.75))
),
by=Period]

periods <- melt(periods, id = 'Period')
periods$variable <- factor(periods$variable, levels = c("p25","p75","median","mean"))

ggplot(data=periods ) +
  geom_line(data=periods, aes(x = Period, y = value, colour = variable, size=variable)) +
  background_grid(major = 'y', minor = "none") +
  scale_colour_manual(values=c("grey","grey","black","royalblue4")) +
  scale_size_manual(values = c(1,1,1.1,1.25)) +
  scale_y_continuous(expand = c(0, 0), limits = c(-1,1), minor_breaks = NULL) +
  xlab(label = "") +
  ylab(label = "Quantity gap") +
  labs(title="Quantity Gap Over Time")
```

**Quantity trade gap across products** 
```{r quantity_products, eval=TRUE}

products <- hs12[, .(mean = as.double(mean(Qty_log_gap)),
                     median = as.double(median(Qty_log_gap)),
                     p25 = as.double(quantile(Qty_log_gap,.25)),
                     p75 = as.double(quantile(Qty_log_gap,.75))
),
by= `Commodity Code`]

ggplot(data=products, aes(mean)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,300), minor_breaks = NULL) +
  labs(title="Mean Quantity Gap Across Products") +
  labs(x="Quantity gap", y="Number of products")

ggplot(data=products, aes(median)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title="Median Quantity Gap Across Products") +
  labs(x="Quantity gap", y="Number of products")

ggplot(data=products, aes(p25)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,200), minor_breaks = NULL) +
  labs(title="25th Percentile Quantity Gap Across Products") +
  labs(x="Trade gap", y="Number of products")

ggplot(data=products, aes(p75)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  scale_y_continuous(expand = c(0, 0), limits = c(0,200), minor_breaks = NULL) +
  background_grid(major = 'y', minor = "none") +
  labs(title="75th Percentile Quantity Gap Across Products") +
  labs(x="Trade gap", y="Number of products")
```

**Quantity trade gap across country pairs** 
```{r quantity_pairs, eval=TRUE}

countries <- hs12[, .(mean = as.double(mean(Qty_log_gap)),
                      median = as.double(median(Qty_log_gap)),
                      p25 = as.double(quantile(Qty_log_gap,.25)),
                      p75 = as.double(quantile(Qty_log_gap,.75))
),
by= c("Importer", "Exporter")]

ggplot(data=countries, aes(mean)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,2000), minor_breaks = NULL) +
  labs(title="Mean Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

ggplot(data=countries, aes(median)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,2500), minor_breaks = NULL) +
  labs(title="Median Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

ggplot(data=countries, aes(p25)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,1500), minor_breaks = NULL) +
  labs(title="25th Percentile Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

ggplot(data=countries, aes(p75)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,2000), minor_breaks = NULL) +
  labs(title="75th Percentile Quantity Gap Across Country Pairs") +
  labs(x="Quantity gap", y="Number of pairs")

rm(periods, products, countries)
```

**Quantity year coefficients controlling for product codes and country pairs** 
```{r quantity_years_reg, eval=TRUE}

hs12$Period <- as.Date(hs12$Period, "%Y")
hs12$Period <- floor_date(hs12$Period,"year")

hs12$Period.f <- factor(hs12$Period)
hs12$Products.f <- factor(hs12$`Commodity Code`)

hs12$Importer.f <- factor(hs12$`Reporter Code`)
hs12$Exporter.f <- factor(hs12$`Partner Code`)
hs12$Pairs.f <- with(hs12, interaction(Importer.f, Exporter.f))

reg <- felm(Qty_log_gap ~ 1 | Period.f + Products.f + Pairs.f,
            data = hs12,
            exactDOF = FALSE,
            keepX = FALSE,
            keepCX = FALSE)

fes <- getfe(reg,
             se=TRUE,
             bN = 50
)

periodfes <- subset(fes,fe == "Period.f")

periodfes$ci_ub <- periodfes$effect + (1.96 * periodfes$se)
periodfes$ci_lb <- periodfes$effect - (1.96 * periodfes$se)
periodfes <- merge(periodfes,unique(hs12[,list(Period,Period.f)]),by.x = "idx",by.y="Period.f")
periodfes <- rename(periodfes, period = Period)

ggplot(data = periodfes, aes(period,effect)) +
  geom_errorbar(aes(ymin = ci_lb, ymax = ci_ub), color = "grey35") +
  geom_line(color = "royalblue4", size = 1) +
  geom_point(color = "royalblue4") +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(-.05, .10), breaks=seq(-.05, .10, .05)) +
  xlab(label = "") +
  ylab(label = "Quantity gap") +
  labs(title = "Quantity Gap Over Time, Controlling for Product/Country Pair")
```

**Quantity product code coefficients controlling for country pairs and years** 
```{r quantity_products_reg, eval=TRUE}

productfes <- subset(fes,fe == "Products.f")
productfes <- productfes[,c("effect","idx")]

ggplot(data=productfes, aes(effect)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,300), minor_breaks = NULL) +
  labs(title="Quantity Gap Across Products, Controlling for Country Pair/Year") +
  labs(x="Quantity gap", y="Number of Products")
```

**Quantity country pair coefficients controlling for years and product codes** 
```{r quantity_pairs_reg, eval=TRUE}

pairfes <- subset(fes,fe == "Pairs.f")
pairfes <- pairfes[,c("effect","idx")]

ggplot(data=pairfes, aes(effect)) +
  geom_histogram(col="royalblue4",
                 fill="royalblue4",
                 alpha=.2) +
  background_grid(major = 'y', minor = "none") +
  scale_y_continuous(expand = c(0, 0), limits = c(0,1500), minor_breaks = NULL) +
  labs(title="Quantity Gap Across Country Pairs, Controlling for Product/Year") +
  labs(x="Quantity gap", y="Number of country pairs")

rm(fes, hs12, pairfes, periodfes, productfes, reg)